\documentclass[12pt]{beamer}
\usepackage[latin1]{inputenc}
\usepackage{fancybox}
\usepackage{soul}
\usepackage{wasysym}
\usecolortheme{wolverine}

\title[]{INF5050 - Protocols and routing in internet}
\subtitle[]{Multiprotocol Label Switching (MPLS) /\newline
			Generalized Multiprotocol Label Switching (GMPLS) }

\author{Khiem-Kim Ho Xuan -- kkho@ifi.uio.no, \newline
		Mattias Håheim Johnsen -- mattiahj@ifi.uio.no}
\date{1. March 2013}
\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}
  \frametitle{Outline}
  \begin{itemize}
  \item Background
  \item MPLS Fundamentals and Terminology
  \item Control and Forwarding Plane
  \item Generalized MPLS
  \item GMPLS Recovery techniques
  \item Summary
  \item Resources
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Background}

  \begin{itemize}
	\item What is MPLS?
		\begin{itemize}
			\item Mechanism that directs data from one network node to the next based on on path labels rather than network addresses.
			\item with such mechanism, we avoid lookups in a routing table
			\item MPLS switches packets (IP packets) instead of routing packets to transport the data
		\end{itemize}
	
	\item Why MPLS?
		\begin{itemize}
			\item Provide a highly scalable mechanism that was topology driven rather than flow driven
			\item Load balance traffic to utilize network bandwidth efficiently
			\item Allow core routers/networking devices to switch packets based on a simplified header
			\item Remove the complexity and overhead of network managements (Assemble and reassemble IP packets)
		\end{itemize}			
	\end{itemize} 

  \bigskip

\end{frame}

\begin{frame}
  \frametitle{MPLS was conceived, why?}
  	\begin{itemize}
  		\item The shortest path routing protocols like IS-IS and OSPF
  			\begin{itemize}
  				\item Did not take capacity characteristics into account while
  				making the routing decisions
  				\item The outcome is, segmentation over the network which leads
  				to congestion, while others remain under-utilized.
  			\end{itemize}
  		\item MPLS reduces the complexity and redundancies by adding new network
  		functionalities.
  	\end{itemize}
\end{frame}

\begin{frame}
  \frametitle{MPLS Fundamentals and Terminology}

  \begin{itemize}
  \item 
    %\pause
  \item 
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{GMPLS}

  \begin{itemize}
  \item What is GMPLS?
  	\begin{itemize}
  		\item  a protocol suite extending MPLS to manage further classes of interfaces and switching technologies other than packet interfaces and switching, such as time division multiplex, layer-2 switch, wavelength switch and fiber-switch.
  	\end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
	\frametitle{GMPLS}
	\begin{itemize}
	

	  		\item GMPLS is an extended form of MPLS and some of these improvements are:
			\begin{itemize}
				\item RSVP-TE
				\item OSPF and IS-IS
				\item New link-management protocol
				\item Bi-directional LSP setup
					\begin{itemize}
						\item Reduce latency
						\item Less control overhead
						\item Route selection is simpler
						\item Cleaner interface
					\end{itemize}									
			\item MPLS emphasizes the seperation of control plane and network plane
			\item GMPLS extends this seperation and allows the control plane to be physically diverse from the associated data plane
				
			\end{itemize}		
				\end{itemize}
\end{frame}





\begin{frame}
  \frametitle{GMPLS: Hierarchial LSP}

  \begin{itemize}
  \item 
    %\pause
  \item 
  \end{itemize}
\end{frame}




\begin{frame}
  \frametitle{Summary}
  \begin{itemize}
  \item MPLS
    %\pause
  \item GMPLS
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Resources}
  \begin{itemize}
  \item Generalized Multiprotocol Label Switching: An Overview of Signaling Enhancements and Recovery Techniques
IEEE Communication Magazine, July 2001.
A. Banerjee et. al. 
  \item Internet Traffic Engineering Using Multi-Protocol Label Switching (MPLS).
Computer Networks 40, Elsevier, 2002
D.O. Awduche and B. Jabbari. 
  \end{itemize}
\end{frame}

\end{document}
